% !TeX spellcheck = en_GB 
\section{Related Work}

\subsection{Interlocking}

\subsubsection{Friction interlocking}

\cite{Duty2019} and \cite{Kazmer2020} consider injecting material from above which spans several layers which are thus joined together.
% pinning layers together using pillars which span multiple layers and which are injected from above.

% Cura 4.8 allows for generating sandwich structures where the layers are alternated between the two materials.

\subsubsection{Dovetail interlocking}

\cite{gouker2006manufacturing} considers the use of 3D dovetail interlocking for multi-material compliant mechanisms.

\cite{debora2020} propose various types of connectors specifically developed for multi-material FDM.

\cite{aharoni2021} consider topology optimization for (2D) interlocking structures.

\cite{malik2017} consider a two-dimensional jigsaw type of interlocking structure.

\cite{Li2013} consider a generalized model for trapezoidal dovetail and friction interlocking.

\cite{Ribeiro2019} consider several 3D printed dovetail designs.

\cite{Wang2021} consider star shaped dovetail interlocking.


\subsubsection{Genus interlocking}

\cite{Rossing2020} develop an interlocking structure, where one material is produced using FDM and the other is produced by overmolding silicone onto the printed part.


Related literature about weaving. e.g. carbon fiber tubes


\subsection{Microstructures}
% multi-material microstructures

\cite{Afshar2016} considers material properties of Polyjet printed solid TPMS.

\cite{Wang2015} propose a dual material auxetic microstructure which unlocks unlocks a new area of material properties compared to single material metamaterials.


\cite{mirzaali2020} explore polyjet printing structures of soft and hard material. % ?

\subsection{Adhesion}
%\citeauthor{tamburrino19} investigate the adhesion between multi-material prints and propose a simple friction based interlocking structure, which consists of straight extrusions of the one material around the other~\cite{tamburrino19}.

\cite{fernandez2019} and \citeauthor{tamburrino19} investigate the adhesion between incompatible materials and the influence of infill pattern and of overlapping toolpaths.

\subsection{Multi-material}
\cite{Zhang2020} explore grading mixing ratios between glass and metal in a custom multi-material SLM machine.

